Robotic Grasping in Clutter Using a Hierarchy of Supervisors for Deep Learning from Demonstrations

### 2016-03-16 paper.tex
added 3 figures

\begin{figure}[t!]
\centering
\includegraphics[width=\columnwidth, height=4cm]{f_figs/robot.pdf}
\caption{ \footnotesize Shown above is a Zymark robot. The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table. The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}
\vspace*{-10pt}
\label{fig:robot}
\end{figure}

@@

\section{Experiments} \label{sec:Exp}

\begin{figure*}[t]
\centering

\includegraphics{f_figs/results.eps}

@@

\subsection{Hierarchical Supervisors}
We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .  We compare having an analytical only supervisor for a fixed amount of data of 160 demonstrations. The non-hierarchical policies trained with the expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.

>>>>

@@

\section{Experiments} \label{sec:Exp}
\begin{figure}[t]
\centering

\includegraphics{f_figs/robot.eps}

\caption{\footnotesize  Shown above is a Zymark robot. The robot consists of an 3DOF arm that lies in a planar workspace and the ability to rotate the turn table. The inscribed circle in the work space prevents the robot from learning the trivial policy of just pushing the objects off the table.}

\label{fig:perf_results}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{f_figs/shapes_set.eps}

\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for. a) Represents states that are easy for the supervisor to provide labels for.  b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
\vspace*{-20pt}
\label{fig:perf_results}
\end{figure}

\begin{figure}[t]
\centering
\includegraphics{f_figs/succes_measure.eps}

\caption{\footnotesize  Examples of different states a supervisor is ask to provide labels for. a) Represents states that are easy for the supervisor to provide labels for.  b) Represents states that are difficult for a human to provide examples and can lead to contradictory examples in similar states }
\vspace*{-20pt}
\label{fig:perf_results}
\end{figure}

@@

\subsection{Hierarchical Supervisors}

\begin{figure*}[t]
\centering
\includegraphics{f_figs/results.eps}

We first test  that using a hierarchy of supervisors can reduce total cost needed to train a policy, but still maintain similar performance .  We compare having an analytical only supervisor for a fixed amount of data of 160 demonstrations. The non-hierarchical policies trained with the expert supervisor only for 160 demonstrations or only the MPIO supervisor for 160 demonstrations.  The policy trained with a hierarchical supervisor first receives  100 demonstrations from the MPIO supervisor and  60 demonstrations from the expert supervisor.
